---
title: "Untitled"
author: "Melinda K. Higgins, PhD."
date: "March 28, 2017"
output: 
  ioslides_presentation:
    css: my.css
    logo: hexsingle1crop.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  margin-left: 40px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>



## Try out some footnotes

Lets assume I have a footnote <footnote content="The first awesoem footnote!">here</footnote>. And here we are going to have another one: <footnote content="This is my second footnote!">#secFN</footnote>


## The Second Topic

See auto numbering for <footnote content = "The counter is not set back and continues on the next slide.">footnotes</footnote>

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

